
\begin{frame}
	\frametitle{Best practices: Data}
	\begin{itemize}[<+-| highlight@+>]
		\item Minimize global and shared data.
		\item Hide information.
		\begin{itemize}
			\item Protects the client by preventing inconsistent state; strenghthens invariants.
			\item Makes client interfaces clear.
			\item Decreases coupling.
			\item Supports future implementation changes.
		\end{itemize}
	\end{itemize}
\end{frame}


\begin{frame}
	\frametitle{Best practices: Programming style}
	\begin{itemize}[<+-| highlight@+>]
		\item Avoid magic numbers and string literals.
		\begin{itemize}
			\item Make semantics clear by assigning the value to a constant with a descriptive name.
			\item Avoid repetition, reuse the same constant. (DRY!)
			\item Avoid implicit dependencies.
			\item Avoid suggestive dependencies.
		\end{itemize}
		\item Avoid long functions and deep nesting.
		\item Prefer build-time errors to run-time errors.
		\item Avoid cyclic dependencies.
	\end{itemize}
\end{frame}


\begin{frame}
	\frametitle{Best practices: Comments}
	\begin{itemize}[<+-| highlight@+>]
		\item Write comments well.
		\item Know what to comment... and what not.
		\item Always document classes and functions using comments.
		\item Document a variable if its meaning is not clear from its name and context.
		\item Add a between-code comment in case the code could work unexpectedly different than it might appear.
		\item Add a between-code comment to document assumptions.
		\item Leave out obvious comments.
		\item Prefer clear code and assertions over comments.
		\item Prefer DRY comments. Don't repeat (parts of) other comments. Don't repeat logic that is already clear from the code.
	\end{itemize}
\end{frame}


\begin{frame}
	\frametitle{Best practices: Design patterns}
	\begin{itemize}[<+-| highlight@+>]
		\item Stand on the shoulders of giants!
		\item Most challenges are generic, with generic solutions already available.
		\item Common vocabulary to use in design discussions.
	\end{itemize}
\end{frame}

